---
title: "parse_pages"
date: '2022-05-30'
---

```{r}
library(tidyverse)
library(pdftools)
library(anytime)
library(reticulate)
source_python("functions.py")
source("~/Projects/nixon-diary-extraction/functions.R")
```

```{r}
raw.1969 <- read_rds("1969.rds")
raw.1970 <- read_rds("1970.rds")
raw.1971 <- read_rds("1971.rds")
raw.1972 <- read_rds("1972.rds")
raw.1973 <- read_rds("1973.rds")
raw.1974 <- read_rds("1974.rds")
```

Appendix pages are incredibly nonstandard. Extracting data from those manually doesn't seem doable.


```{r}
toc_1969 <- build_toc("1969 Presidential Daily Diary.pdf")
toc_1970 <- build_toc("1970 Presidential Daily Diary.pdf")
toc_1971 <- build_toc("1971 Presidential Daily Diary.pdf")
toc_1972 <- build_toc("1972 Presidential Daily Diary.pdf")
toc_1973 <- build_toc("1973 Presidential Daily Diary.pdf")
toc_1974 <- build_toc("1974 Presidential Daily Diary.pdf")
```


```{r}
diary.1969 <- create.doc.lists(raw.1969, toc_1969)
diary.1970 <- create.doc.lists(raw.1970, toc_1970)
diary.1971 <- create.doc.lists(raw.1971, toc_1971)
diary.1972 <- create.doc.lists(raw.1972, toc_1972)
diary.1973 <- create.doc.lists(raw.1973, toc_1973)
diary.1974 <- create.doc.lists(raw.1974, toc_1974)
```

The colon is sometimes recognized as a 3. Also sometimes "10:xx" becomes "0:xx". Write time validation function after processing. There's 1 - 3 characters between times. Also

```{r}
test <- diary.1971$`April 17, 1971`$pages[1]
test_split <- str_split(test, '\\n')[[1]]
str_match(test_split[29], paste0("(", time_pattern, ")", "\\D*", "(", time_pattern, ")", "\\W*", "(", call_pattern, ")", "\\W*"))
```





```{r}
test_df <- build_data_frame("April 17, 1971", diary.1971$`April 17, 1971`$pages)
```


Steps:
Find the first line item (str_starts)
get time, P|R, rest of text
while next line not new item, append


TODO:
Fix the phone regex capturing the P in people's names
Store whole dataframe in diary object
Deal with items where there's just a line that is "The President:" and the next item is just names of meetings
Write Time validation logic 
Drop "The PResident Met with:" At end of lines